---
title: "Assignment6"
output: html_document
date: "2022-11-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Get the samples using rnorm and calculate the KS


```{r}
X <- rnorm(10^5)
F_hat <- ecdf(X)
F_hat_eval <- F_hat(sort(X))
F_eval <- pnorm(sort(X))
KS_stats1 <- max(abs(F_hat_eval - F_eval))

```
Box-Muller method
```{r}
U1 <- runif(10^5)
U2 <- runif(10^5)

Z1 <- sqrt(-2*log(U1))*cos(2*pi*U2)

F_hat <- ecdf(Z1)
F_hat_eval <- F_hat(sort(Z1))
F_eval <- pnorm(sort(Z1))
KS_stats2 <- max(abs(F_hat_eval - F_eval))

```
Rejection and Acceptance

```{r}
# install.packages('ExtDist')
library('ExtDist')
smt <- rLaplace(10^5)
c1 <- 3

U3 <- runif(10^5)
lapla <- dLaplace(smt)
Norm <- dnorm(smt)
thresh <- Norm/(c1*lapla)

sample <- smt[U3<thresh]

F_hat <- ecdf(sample)
F_hat_eval <- F_hat(sort(sample))
F_eval <- pnorm(sort(sample))
KS_stats3 <- max(abs(F_hat_eval - F_eval))

```
Start comparing
```{r}
print('Output by dnorm')
print(KS_stats1)
print('Output by Box Muller')
print(KS_stats2)
print('Output by Reject and Accept')
print(KS_stats3)
```

We can see that dnorm gives the lowest KS-test, which means they are closest to the Normal, which should be reasonable. The second one is Box-Muller, with not much different to dnorm. However, the results output by Reject and Accept is the largest value, suggesting they are the most different. This can be due to a smaller smaple size, as the process rejects some samples, making the data smaller. Another unseen reason is the KS-test being sensitive to outliers, and thus, we cannot be sure